Reflections from reproductions

### 2024-10-11 pages/paper_evaluation.qmd
docs(evaluation): add spaces for hernandez and wood results

@@

<!-- TODO: Add Johnson et al. 2021 -->

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 6, 3, 1],
  'Lim et al. 2020': [16, 2, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
  'Huang et al. 2019': [7, 2, 7, 2],
  'Lim et al. 2020': [12, 0, 4, 2],
  'Kim et al. 2021': [12, 0, 5, 1],
  'Anagnostou et al. 2022': [8, 3, 4, 3],
  'Johnson et al. 2021': [0, 0, 0, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>

@@

<!-- TODO: Add Johnson et al. 2021, and update after discussion of Kim et al. 2021 -->

| Item | S | H | L | K | A | J |
| - | - | - | - | - | - | - | - |

@@

: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}

@@

* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>

<!-- TODO: Add Johnson -->

| Item | S | H | L | K | A | J |
| - | - | - | - | - | - | - | - |

@@

<!-- TODO: Add johnson -->

* @shoaib_simulation_2021 - 1h 56m
* @huang_optimizing_2019 - 1h 28m
* @lim_staff_2020 - 1h 12m
* @kim_modelling_2021 - 2h 12m
* @anagnostou_facs-charm_2022 - 53m
* @johnson_cost_2021

>>>>

Consider: **What criteria are people struggling to meet from the guidelines?**

@@

<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 -->

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 6, 3, 1],
  'Lim et al. 2020': [16, 2, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [0, 0, 0, 1]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
  'Huang et al. 2019': [7, 2, 7, 2],
  'Lim et al. 2020': [12, 0, 4, 2],
  'Kim et al. 2021': [12, 0, 5, 1],
  'Anagnostou et al. 2022': [8, 3, 4, 3],
  'Johnson et al. 2021': [0, 0, 0, 1],
  'Hernandez et al. 2015': [10, 0, 8, 0],
  'Wood et al. 2021': [0, 0, 0, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>
* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reporting.html#stress-des" target="_blank">link to evaluation</a>

@@

<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |

@@

: {tbl-colwidths="[60, 5, 5, 5, 5, 5, 5, 5, 5]"}

@@

* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **Hu:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **He:** @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>
* **W:** @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reporting.html#des-checklist-derived-from-ispor-sdm" target="_blank">link to evaluation</a>

<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021, and update after discussion of Kim et al. 2021 -->

| Item | S | Hu | L | K | A | J | He | W |
| - | - | - | - | - | - | - | - | - | - |

@@

<!-- TODO: Add johnson, hernandez, wood -->

* @shoaib_simulation_2021 - 1h 56m
* @huang_optimizing_2019 - 1h 28m
* @lim_staff_2020 - 1h 12m
* @kim_modelling_2021 - 2h 12m
* @anagnostou_facs-charm_2022 - 53m
* @johnson_cost_2021
* @hernandez_optimal_2015
* @wood_value_2021

### 2024-10-11 pages/reflections.qmd
docs(evaluation): add spaces for hernandez and wood results

<!--TODO: Add Johnson et al. 2021 reflections once have finished reproduction -->

@@

* @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reflections.html" target="_blank">link to reflections</a>
* @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reflections.html" target="_blank">link to reflections</a>
* @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
* @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> |

@@

**Reflections:** Large amounts of code duplication are non-ideal as they can:

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> |

>>>>

<!--TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 reflections once have finished reproduction -->

@@

* @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reflections.html" target="_blank">link to reflections</a>
* @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reflections.html" target="_blank">link to reflections</a>
* @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
* @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
* @hernandez_optimal_2015 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reflections.html" target="_blank">link to reflections</a>
* @wood_value_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reflections.html" target="_blank">link to reflections</a>

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@hernandez_optimal_2015: <!--TODO-->

@wood_value_2021: <!--TODO-->

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | 🟡 | ❌ | ✅ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | ✅ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

@hernandez_optimal_2015: <!--TODO-->

@wood_value_2021: <!--TODO-->

**Reflections:** <!--TODO: Update reflections (since have added Johnson, Hernandez and Wood) --> Large amounts of code duplication are non-ideal as they can:

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | 🟡 | 🟡 | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| N/A | N/A | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| 🟡 | ❌ | 🟡 | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> | <!--TODO--> | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 | @hernandez_optimal_2015 | @wood_value_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> | <!--TODO--> | <!--TODO--> |
